D3064R0: How to Avoid OOTA Without Really Trying

### 2024-02-25 ootavacuous.tex
Rename "Additional Litmus Tests" to "Illustrative Litmus Tests"
Signed-off-by: Paul E. McKenney <paulmck@kernel.org>

The earlier examples shown in
Listings~\ref{lst:Simple Reordering}
and~\ref{lst:Simple OOTA}
can be recast as similar \co{herd7} litmus tests, as shown in
Listing~\ref{lst:Simple Reordering as Litmus Test}
on page~\pageref{lst:Simple Reordering as Litmus Test}
and Listing~\ref{lst:Causality Test Case 4}
on page~\pageref{lst:Causality Test Case 4}, respectively.
Other OOTA-related litmus tests may be found in
Appendix~\ref{app:Litmus Tests from “Causality Test Cases"}
and
Appendix~\ref{app:Additional Litmus Tests}.

@@

\section{Additional Litmus Tests}
\label{app:Additional Litmus Tests}

>>>>

The earlier examples shown in
Listings~\ref{lst:Simple Reordering}
and~\ref{lst:Simple OOTA}
can be recast as similar \co{herd7} litmus tests, as shown in
Listing~\ref{lst:Simple Reordering as Litmus Test}
on page~\pageref{lst:Simple Reordering as Litmus Test}
and Listing~\ref{lst:Causality Test Case 4}
on page~\pageref{lst:Causality Test Case 4}, respectively.
Other OOTA-related litmus tests may be found in
Appendix~\ref{app:Litmus Tests from “Causality Test Cases"}
and
Appendix~\ref{app:Illustrative Litmus Tests}.

@@

\section{Illustrative Litmus Tests}
\label{app:Illustrative Litmus Tests}
